Optimal (Multiway) Spatial Joins

### 2024-05-23 msj.tex
yufei

\noindent {\bf Step 1.} We will accomplish this step by solving an instance of $(k-2)$-SJ constructed as follows. For each rectangle $r_1 \in R_1$, we compute four segments:
\myitems{
    \item $h_1$: the lowest segment (i.e., with the smallest y-coordinate) among all the segments in $H$ that cross $r$;
    \item $h_2$: the highest segment (i.e., with the largest y-coordinate) among all the segments in $H$ that cross $r$;
    \item $v_1$: the leftmost segment (i.e., with the smallest x-coordinate) among all the segments in $V$ that cross $r$;
    \item $v_2$: the rightmost segment (i.e., with the largest x-coordinate) among all the segments in $V$ that cross $r$.
}
Define $r_1'$ the rectangle defined by the above four segments in the way illustrated in Figure~\ref{fig:four-segs}, where $r_1'$ is the shaded area. Note that $r_1'$ exists if and only if $r_1$ is crossed by at least one horizontal segment in $H$ and by at least one vertical segment in $V$. Moreover, it is possible for $h_1$ and $h_2$ to be the same segment (same for $v_1$ and $v_2$). Define
\myeqn{
    R_1' &=& \set{r_1' \mid r_1 \in R_1 \text{ and its $r_1'$ defined as above exists}}. \nn
}
Computing the corresponding ``segment $h_1$'' for each $r_1 \in R_1$ is an instance of Problem $\EuScript{A}$. By symmetry, so is the computation of $h_2, v_1$, and $v_2$ segments for each $r_1 \in R_1$. It thus follows from Section~\ref{sec:bricks} that $R_1'$ can be produced in $O(n \log n)$ time and $O(n)$ space.

>>>>

\noindent {\bf Step 1.} We will accomplish this step by solving an instance of $(k-2)$-SJ constructed as follows. For each rectangle $r_1 \in R_1$, we compute four segments:
\myitems{
    \item $h_1$: the lowest segment (i.e., with the smallest y-coordinate) among all the segments in $H$ that cross $r$;
    \item $h_2$: the highest segment (i.e., with the largest y-coordinate) among all the segments in $H$ that cross $r$;
    \item $v_1$: the leftmost segment (i.e., with the smallest x-coordinate) among all the segments in $V$ that cross $r$;
    \item $v_2$: the rightmost segment (i.e., with the largest x-coordinate) among all the segments in $V$ that cross $r$.
}
Define $r_1'$ as the rectangle defined by the above four segments in the way illustrated in Figure~\ref{fig:four-segs}, where $r_1'$ is the shaded area. Note that $r_1'$ exists if and only if $r_1$ is crossed by at least one horizontal segment in $H$ and by at least one vertical segment in $V$. Moreover, it is possible for $h_1$ and $h_2$ to be the same segment; same for $v_1$ and $v_2$. Define
\myeqn{
    R_1' &=& \set{r_1' \mid r_1 \in R_1 \text{ and its $r_1'$ defined as above exists}}. \nn
}
Computing the corresponding ``segment $h_1$'' for each $r_1 \in R_1$ is an instance of Problem $\EuScript{A}$. By symmetry, so is the computation of $h_2, v_1$, and $v_2$ segments for each $r_1 \in R_1$. It thus follows from Section~\ref{sec:bricks} that $R_1'$ can be produced in $O(n \log n)$ time and $O(n)$ space.

We now solve the $(k-2)$-SJ problem on $R_1', R_2, ..., R_{k-2}$ using the algorithm $\A$ supplied. Let us represent the result of this $(k-2)$-SJ as $\J(R_1', R_2, ..., R_{k-2})$. The following observation is crucial.

\begin{lemma} \label{sec:hv:type1:proj}
    A $(k-2)$-tuple $(r_1', r_2, ..., r_k)$ exists in $\J(R_1', R_2, ..., R_{k-2})$ if and only if the $(k-2)$-tuple $(r_1, r_2, ..., r_k)$ exists in $\Pi_{1:k-2}(\J_1(R_1, ...,$ $R_{k-2}, H, V))$, where $r_1$ is the rectangle in $R_1$ defining $r_1'$.
\end{lemma}
